A Taxonomy of Twists of Supersymmetric Yang--Mills Theory -- Comments on Referee Report

### 2022-03-01 paper_journal_edits.tex
started responding to ref report

\begin{prop}
Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}. The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
\label{prop:mapintocotangent}
\end{prop}
\begin{proof}
The claim follows from the following isomorphisms of graded vector bundles:
\begin{align*}
\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
\end{align*}
\end{proof}

@@

\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ defined by
\[\alpha\otimes \beta \mapsto \int_M \omega( \alpha, \beta)\]
is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
\end{enumerate}
\end{definition}

@@

@@

\begin{definition}
Let $X,Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an integer $m$ and suppose $X$ is equipped with an $m$-th root of the canonical bundle $K_X^{1/m}$. Let $\fg$ be an $L_\infty$ algebra equipped with a $\ZZ$-grading $\fg=\bigoplus_n \fg(n)$ and equipped with a symmetric pairing $\langle -, -\rangle$ as before, which has weight $m$ with respect to the grading. Then the generalized Chern--Simons theory is the classical field theory
\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} K_X^{1/m}).\]
\label{def:sectChernSimons}
\end{definition}

@@

Under the composition
\[\Omega^\bullet(V_\RR; \CC)\xto{p^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
defined by pulling back forms along $p$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component. 
This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
\end{proof}

@@

We may identify $\wedge^2(V)\rightarrow \so(V)$ via
\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
This gives rise to an action map
\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
of two-forms on spinors.

@@

We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$. Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
\[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]

@@

\begin{prop}
Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(N, \Sigma)$. Then
\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
\label{prop:cliffordactionproperty2}
\end{prop}

@@

In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing, which should be thought of as the complexified Lie algebra of the gauge group.

>>>>

\begin{prop}
Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}. The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
\label{prop:mapintocotangent}
\end{prop}
\begin{proof}
The claim follows from the following isomorphisms of graded vector bundles:
\begin{align*}
\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)],
\end{align*}
where the superscript $!$ refers to the $\Dens_M$ valued dual space: $\mc E^! = \mc E^\vee \otimes \Dens_M$.
\end{proof}

@@

\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ on the space of compactly supported sections of $L$ defined by
\[\alpha\otimes \beta \mapsto \int_M \omega( \alpha, \beta)\]
is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
\end{enumerate}
\end{definition}

@@

\begin{remark}
This definition is extremely broad, for instance the complex $\cL$ of fields can have cohomology in any degree.  In specific applications to quantum field theory one is likely to encounter examples that are more heavily restricted by assumptions about the existence of a quantization with certain properties.
\end{remark}

@@

\begin{definition}
Let $X,Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an integer $m$ and suppose $X$ is equipped with a $j$-th root of the canonical bundle $K_X^{1/j}$. Let $\fg$ be an $L_\infty$ algebra equipped with a $\ZZ$-grading $\fg=\bigoplus_n \fg(n)$ and equipped with a symmetric pairing $\langle -, -\rangle$ as before, which has weight $j$ with respect to the grading. Then the generalized Chern--Simons theory is the classical field theory
\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} K_X^{1/j}).\]
\label{def:sectChernSimons}
\end{definition}

@@

Under the composition
\[\Omega^\bullet(V_\RR; \CC)\xto{\mr{Re}^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
defined by pulling back forms along $\mr{Re}$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component. 
This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
\end{proof}

@@

We may identify $\wedge^2(V)\rightarrow \so(V)$ via the map
\[\omega\mapsto (v\mapsto -2\iota_{v^*} \omega),\]
where $v$ is an element of $V$ and $\iota_{v^*}$ is the contraction with the associated element $v^* = (v,-)$ of $V^*$ induced by the bilinear pairing.  This gives rise to an action map
\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
of two-forms on spinors.

@@

We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$. Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as described above we have the associated Dirac operator
\[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]

@@

\begin{prop}
Suppose $Q_1,Q_2$ and $\lambda\in\Gamma(N, \Sigma)$. Then
\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
\label{prop:cliffordactionproperty2}
\end{prop}

@@

In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing, which should be thought of as the complexified Lie algebra of the gauge group.  We will refer to the classification of twisting supercharges from \cite{ElliottSafronov} throughout.

### 2022-03-01 twist_selecta_referee_comments.tex
started responding to ref report

\begin{enumerate}
 \item Page 8:
 \item Page 18:
 \item Page 20 points 1 and 2:
 \item Page 20 point 3:
 \item Page 28:
 \item Page 29
 \item Page 32:
 \item Page 34 point 1:
 \item Page 34 point 2:
 \item Page 35:
 \item Page 36:
 \item Page 37:
 \item Page 38:
 \item Page 51:
 \item Page 52:
 \item Page 54:
 \item Page 56:
\end{enumerate}

>>>>

\begin{enumerate}
 \item Page 8: Added an explanatory comment.
 \item Page 18:
 \item Page 20 points 1 and 2: Some further explanation was added for the notation here.
 \item Page 20 point 3: Added a remark, thank you.
 \item Page 27:
 \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
 \item Page 32:
 \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part}
 \item Page 34 point 2:
 \item Page 35: Added some clarification to the notation here.
 \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
 \item Page 37:
 \item Page 38:
 \item Page 51: Thank you, reference added.
 \item Page 52:
 \item Page 54:
 \item Page 56:
\end{enumerate}
